---
title: "Module 7 - Codethrough"
author: "Thomas O'Dell"
date: "2025-02-27"
output: html_document
---

## Interactive Map Tutorial

#### This Code-through demonstrates how to create an interactive map using the giscoR API from the European Geographic Information System of the Comission (GISCO).

#### The map can be customized to showcase up to 4 administrative levels known as Nomenclature of Territorial Units for Statistics (NUTS). These levels will vary by country but generally will adhere to the following structure:

-   **NUTS 0** → **Country**

-   **NUTS 1** → **Geographical Regions**

-   **NUTS 2** → **Provinces**

-   **NUTS 3** → **Large Cities or Counties**

### At a high level, the steps are as follows:

#### - Install and load tidyverse, giscoR, and ggiraph packages

#### - Determine desired NUTS level, and define objects using the gisco_get_nuts function. For European countries you can simply enter the country name to ensure the correct data is pulled. 

#### - Input NUTS level, desired year(s), and map projection (EPSG 3035 is used in this case, as that is the optimal projection for Europe) 

#### - Associate gg_plt with your defined NUTS levels (e.g. "Provinces". Define aesthetics (aes) and any thematic elements (e.g. border line width and color) 

#### - Associate ggobj with gg_plt to ensure the girafe (graphing function) works appropriately 

#### - Knit! 

***

#### The process is further detailed in the code below is the Step-by-step process

***

```{r setup, include=FALSE}

#Load Packages
library(tidyverse)
library(giscoR)

```

#### STEP 1: Load Packages

```{r}
library(tidyverse)
library(giscoR)
```

#### STEP 2:

#### - Name and Define NUTS levels

#### - Define year and map projection

```{r}
italy_municipalities <- gisco_get_nuts(
  country = 'Italy',
  nuts_level = '3',
  year = "2024",
  epsg = 3035
) |>
  as.tibble() |>
  janitor::clean_names()
```

#### STEP 3: Name and Define any additional NUTS levels

```{r}
italy_regions <- gisco_get_nuts(
  country = 'Italy',
  nuts_level = 1,
  year = "2024",
  epsg = 3035
) |>
  as.tibble() |>
  janitor::clean_names()
```

#### STEP 4: Load Additional packages

```{r}
library(ggplot2)
library(ggiraph)
```

#### STEP 5:

#### - Associate gg_plt with your name for desired NUTS level

#### - Define geometry

#### - Define additional desired data

#### - Define any thematic elements such as color or font

#### - Make any design decisions (e.g. I chose to omit the legend, though it comes standard with giscoR)

```{r}
gg_plt <- italy_municipalities |>
  ggplot(aes(geometry = geometry)) +
  geom_sf(
    data = italy_regions,
    aes(fill = nuts_name),
    color = 'black',
    linewidth = 0.5
  ) +
  geom_sf_interactive(
    fill = NA,
    aes(
      data_id = nuts_id,
      tooltip = nuts_name
    ),
    color = 'black',
    linewidth = 0.1
  ) + 
  theme_void() +
  theme(legend.position = 'none')

girafe(ggobj = gg_plt)

```

### Final Thoughts

These simple steps with the comprehensive giscoR API allows users to rapidly generate detailed and very customizeable maps. The pre-defined NUTS levels allow users to adjust the level of detail to their purposes and the interactive map with tooltip provides a pleasing user experience.

This package is specific to Europe, feel free to try it yourself with your country of choice!

<br><br><br><br>
